---
title: "In situ data"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(fs)
library(glue)
library(httr)
library(jsonlite)
library(lubridate)
library(vroom)
```

# Get surface water chem data

Searching NEON API for files within a data product. Files are saved in Box

```{r, eval = FALSE}
source('R/myfxns.R')
source('R/my-aos-fxns.R')
chem_dir <- '~/Box/data/NEON/NEON_chem-surfacewater'
lake_river_sites <- c('BARC', 'SUGG', 'CRAM', 'LIRO', 'PRPO', 'PRLA', 'TOOK', 'FLNT', 'BLWA', 'TOMB', 'BLUE')

lake_river_sites %>% purrr::walk(~update_phyto_files(.x, myglob = 'alg_fieldData'))
lake_river_sites %>% purrr::walk(~update_phyto_files(.x, 'algaeExternalLabDataPerSample'))

lake_river_sites %>% purrr::walk(~update_swchem_files(.x, myglob = 'externalLabData'))
lake_river_sites %>% purrr::walk(~update_swchem_files(.x, myglob = 'fieldSuperParent'))
lake_river_sites %>% purrr::walk(~update_swchem_files(.x, myglob = 'swc_fieldData'))
```

# Sampling Dates

once things are updated and downloaded, make a table of all sites and sampling dates

```{r, eval = FALSE}
get_aos_dates <- function(mysite){
  fsp_files <- fs::dir_ls(glue('{chem_dir}/{mysite}'), glob = "*swc_fieldData*")
  fsp_df <- fsp_files %>% purrr::map_df(~read_csv(.x)) # update to vroom? 
  fsp_df_sub <- fsp_df %>% 
    dplyr::select(domainID, siteID, namedLocation, collectDate, 
                sampleID, replicateNumber)
  field_sample_dates_df <- fsp_df_sub %>% 
    mutate(collect_date = lubridate::as_date(collectDate)) %>% 
    mutate(collect_datetime = collectDate) %>% 
    dplyr::select(domainID, siteID, namedLocation, collect_date, collect_datetime) %>%
    distinct()
  return(field_sample_dates_df)
}
aos_dates_df <- lake_river_sites %>% purrr::map_dfr(~get_aos_dates(.x))
aos_dates_df <- aos_dates_df %>% 
  mutate(loctype = str_sub(namedLocation, 10, nchar(namedLocation))) %>%
  mutate(loctype4 = str_sub(loctype, 1, 4))
```

## Surface water chemistry

Get data for a selected analyte

```{r}
get_values_site_swchem <- function(my_siteid, my_analyte){
  chem_dir <- '~/Box/data/NEON/NEON_chem-surfacewater'
  lab_files <- fs::dir_ls(glue('{chem_dir}/{my_siteid}'), glob = "*externalLab*")
  chem_df <- lab_files %>% vroom::vroom(delim = ',')
  site_values <- chem_df %>% dplyr::filter(analyte %in% my_analyte)
  site_values_simp <- site_values %>% 
    dplyr::select(uid, domainID, siteID, namedLocation, collectDate,
                  analyte, analyteConcentration, analyteUnits, sampleCondition)
  return(site_values_simp)
}
```

```{r}
my_siteid <- "PRPO"
```

```{r}
my_analytes <- c('TSS', 'TDS', 'DOC', 'TOC', 'Fe', 
                 'UV Absorbance (250 nm)', 'UV Absorbance (254 nm)',
                 'UV Absorbance (280 nm)')
site_chem_df <- get_values_site_swchem(my_siteid, my_analytes)
site_chem_df <- site_chem_df %>%
  dplyr::mutate(analyte = dplyr::case_when(analyte == 'UV Absorbance (250 nm)' ~ 'UV Absorbance (254 nm)',
                                           TRUE ~ analyte))


```

read in aop dates for site 

```{r}
cell_info_join <- read_csv('../spectra/results/l1-info.csv')
cell_info_site <- cell_info_join %>% dplyr::filter(siteID == my_siteid)

aop_dates <- cell_info_site %>% 
  dplyr::select(siteID, flightdate, clouds, nmdLctn) %>%
  rename(namedLocation = nmdLctn)
```

```{r}
# site_chem_df
```

```{r}
gg <- site_chem_df %>%
  ggplot(aes(x = as_date(collectDate), y = analyteConcentration)) +
  facet_grid(vars(analyte), vars(namedLocation), scales = 'free_y') +
  # facet_wrap(vars(analyte), scales = 'free_y') +
  theme_bw() +
  coord_cartesian(ylim = c(0, NA)) +
  theme(legend.position = 'bottom', legend.box="vertical") +
  ggtitle(glue('{my_siteid} AOS sampling - surface water chem')) +
  geom_vline(data = aop_dates, aes(xintercept = flightdate, col = clouds)) +
  scale_color_manual(values = list("Green (<10%) cloud cover" = "green", 
                                   "Red (> 50%) cloud cover" = "red", 
                                   "Yellow (10 - 50%) cloud cover" = "orange")) +
  geom_line(col = 'gray') +
  geom_point(aes(fill = sampleCondition), pch = 21, size = 2) +
  scale_fill_viridis_d() +
  xlab(element_blank())
gg
ggsave(glue('figs/{my_siteid}-AOSxAOP.png'), width = 12, height = 8)
```

time difference is the number of days before (-) or after (+) the flight time that the grab sampling occurred

GO through with CRAM or TOOK or LIRO where there are multiple buoy depths to pull all buoy samples/reps

```{r}
# my_siteid <- "BARC"
# site_spectra_df <- readxl::read_excel('../spectra/results/Master.xlsx', 
#                                       sheet = 'SpectraPixels-2') %>% 
#   dplyr::filter(siteID == my_siteid)
# cell_info_join <- read_csv('../spectra/results/l1-info.csv')
# cell_info_site <- cell_info_join %>% dplyr::filter(siteID == my_siteid)
```

```{r}
# site_spectra_df$spectraID[1]
# spectra_id <- 'BLUE-S2-20170506_160715'
# str_split(spectra_id, "-", simplify = TRUE)[,2]
# my_analyte <- 'DOC'
# cell_info_site[1,]
# spectra_id = 1
# spectra_loc <- cell_info_site[['nmdLctn']][spectra_id]
# spectra_date <- cell_info_site[['flightdate']][spectra_id]

get_closest_sample <- function(spectra_id, my_analyte){
  spectra_date <- cell_info_site[['flightdate']][spectra_id] %>% as_date()
  spectra_loc <- cell_info_site[['nmdLctn']][spectra_id]
  
  my_df <- site_chem_df %>% 
    dplyr::filter(analyte == my_analyte) %>%
    dplyr::filter(str_detect(namedLocation, spectra_loc)) %>%
    mutate(collectDateDate = as_date(collectDate))
# probably wont work if there are replicates
# or when multiple buoy depths
  min_id <- abs(spectra_date - my_df$collectDateDate) %>% which.min()
  my_samp <- my_df[min_id,] %>% 
    mutate(timediff = collectDateDate - spectra_date) %>%
    dplyr::select(-uid) %>% mutate(spectra = spectra_id)
  return(my_samp)
}

# match_df <- my_analytes %>% purrr::map_df(~get_closest_sample('BARC-buoy-20140507_152342', .x))

```

> TODO: fix to work with spectra pixels spreadsheet

```{r}
match_inputs <- tidyr::expand_grid(1:nrow(cell_info_site), my_analytes) %>%
  dplyr::rename(spectraID = 1, analyte = 2)
match_df <- purrr::map2_dfr(.x = match_inputs$spectraID,
                            .y = match_inputs$analyte,
                            .f = ~get_closest_sample(.x, .y))
```

```{r}
# match_df %>% 
#   dplyr::select(c(3:8,10)) %>%
#   filter(namedLocation == 'PRPO.AOS.buoy.c0') %>% 
#   distinct() %>%
#   arrange(analyte, collectDate) %>% View()
```

```{r}
match_df %>% write_csv(glue('results/spectra-matches/{my_siteid}-spectra-matches.csv'))

```

## secchi depth

```{r}
secchi_df <- fs::dir_ls('results/secchi-x-site') %>%
  purrr::map_dfr(~read_csv(.x)) %>%
  dplyr::select(domainID, siteID, namedLocation, date, clearToBottom, 
                maxDepth, euphoticDepth, icePresent, secchiMeanDepth, remarks) %>%
  mutate(datedate = lubridate::as_date(date))
```

```{r}
# spectra_df <- readxl::read_excel('../spectra/results/spectra-ids.xlsx', sheet = 'SpectraPixels')
```

```{r}
# my_spectra_id = 1
# spectra_df$flightdate[my_spectra_id]
# spectra_df$nmdLctn[my_spectra_id]
# spectra_df$radfile[my_spectra_id]

get_closest_secchi <- function(my_spectra_id){
  spectra_date <- cell_info_join$flightdate[my_spectra_id] %>% as_date()
  spectra_loc <- cell_info_join$nmdLctn[my_spectra_id]
  my_radfile <- cell_info_join$radfile[my_spectra_id]
  my_df <- secchi_df %>% 
    dplyr::filter(namedLocation %in% spectra_loc)
# probably wont work if there are replicates
# or when multiple buoy depths
  min_id <- abs(spectra_date - my_df$datedate) %>% which.min()
  my_samp <- my_df[min_id,] %>% 
    mutate(timediff = datedate - spectra_date) %>% mutate(radfile = my_radfile)
  return(my_samp)
}
secchi_matches <- 1:nrow(cell_info_join) %>% purrr::map_dfr(~get_closest_secchi(.x))
secchi_matches %>% write_csv('results/secchi-matches.csv')
```

## chlorophyll a in situ data

No (good) AOS chlorophyll a data prior to late 2017. 

phytoplankton sampling and taxonomy

Join lab and field data to get sampling positions

```{r}
phyto_dir2 <- '~/Box/data/NEON-processed/chl-a'
lake_river_sites %>% purrr::walk(~join_field_and_lab(.x))
```

```{r}
chla_analytes <- c('chlorophyll a', 'pheophytin', 'total cholorophyll a')

get_chla_site <- function(mysite, my_analytes){
  my_files <- fs::dir_ls(phyto_dir2, glob = glue("*{mysite}*"))
  chla_coltypes <- cols(
    domainID = col_character(),
    siteID = col_character(),
    namedLocation = col_character(),
    collectDate = col_date(format = ""),
    sampleID = col_character(),
    sampleCondition = col_character(),
    replicate = col_double(),
    analyte = col_character(),
    analyteConcentration = col_double(),
    plantAlgaeLabUnits = col_character(),
    externalLabDataQF = col_character(),
    parentSampleID = col_character(),
    aquaticSiteType = col_character(),
    collect_date = col_date(format = ""),
    time_hms = col_time(format = ""),
    habitatType = col_character(),
    algalSampleType = col_character(),
    phytoDepth1 = col_double(),
    phytoDepth2 = col_double(),
    phytoDepth3 = col_double(),
    substratumSizeClass = col_character())
  phyto_df <- read_csv(my_files, col_types = chla_coltypes)
  site_values <- phyto_df %>% dplyr::filter(analyte %in% my_analytes)
  site_values_simp <- site_values
  return(site_values_simp)
}

phyto_df <- lake_river_sites %>% purrr::map_dfr(~get_chla_site(.x, chla_analytes))

phyto_df$algalSampleType %>% table()
phyto_df_sub <- phyto_df %>% 
  dplyr::filter(algalSampleType %in% c('seston', 'phytoplankton'))

# phyto_df_sub$externalLabDataQF %>% table()
```

```{r}
my_siteid <- 'BARC'
cell_info_join <- read_csv('../spectra/results/l1-info.csv')
cell_info_site <- cell_info_join %>% dplyr::filter(siteID == my_siteid)

aop_dates <- cell_info_site %>% 
  dplyr::select(siteID, flightdate, clouds, nmdLctn) %>%
  rename(namedLocation = nmdLctn)

phyto_df_mysite <- phyto_df_sub %>% dplyr::filter(siteID == my_siteid) 

# phyto_df_mysite %>%
#    ggplot(aes(x = as_date(collectDate), y = analyteConcentration)) +
#   facet_grid(vars(analyte), vars(namedLocation), scales = 'free_y') +
#   # facet_wrap(vars(analyte), scales = 'free_y') +
#   theme_bw() +
#   coord_cartesian(ylim = c(0, NA)) +
#   theme(legend.position = 'bottom', legend.box="vertical") +
#   ggtitle(glue('{my_siteid} AOS sampling - chlorophyll')) +
#   geom_vline(data = aop_dates, aes(xintercept = flightdate, col = clouds)) +
#   scale_color_manual(values = list("Green (<10%) cloud cover" = "green", 
#                                    "Red (> 50%) cloud cover" = "red", 
#                                    "Yellow (10 - 50%) cloud cover" = "orange")) +
#   geom_line(col = 'gray') +
#   geom_point(aes(fill = sampleCondition), pch = 21, size = 2) +
#   scale_fill_viridis_d() +
#   xlab(element_blank()) +
#   expand_limits(xmin = min(aop_dates$flightdate), xmax = max(aop_dates$flightdate))
#   
# ggsave(glue('figs/{my_siteid}-AOSxAOP-chl.png'), width = 9, height = 5)

```

```{r}

spectra_id = 1
spectra_loc <- cell_info_site[['nmdLctn']][spectra_id]
spectra_date <- cell_info_site[['flightdate']][spectra_id]
my_analyte <- 'chlorophyll a'
# get_closest_sample <- function(spectra_id, my_analyte){
  spectra_date <- cell_info_site[['flightdate']][spectra_id] %>% as_date()
  spectra_loc <- cell_info_site[['nmdLctn']][spectra_id]
  
  my_df <- phyto_df_mysite %>% 
    dplyr::filter(analyte == my_analyte) %>%
    dplyr::filter(str_detect(namedLocation, spectra_loc)) %>%
    mutate(collectDateDate = as_date(collectDate))
# probably wont work if there are replicates
# or when multiple buoy depths
  min_id <- abs(spectra_date - my_df$collectDateDate) %>% which.min()
  my_samp <- my_df[min_id,] %>% 
    mutate(timediff = collectDateDate - spectra_date) %>%
    mutate(spectra_date = spectra_date)
  return(my_samp)
# }
```


## sensor data

then same for sensor data



